---
title: "Get TCGA Case IDs from File UUIDs"
author: "Leo Williams"
output:
  html_document:
    toc: yes
params:
  # Variables
  output_dir: ""
  gdc_manifest_file: ""
---

# About

This workflow is adapted from the article [GenomicDataCommons Example: UUID to TCGA and TARGET Barcode Translation](https://seandavi.github.io/post/2017-12-29-genomicdatacommons-id-mapping/) and uses the `GenomicDataCommons` R Bioconductor package.

# Setup

```{r setup}
# Load packages 
library(knitr)
library(tidyverse)
library(GenomicDataCommons)

# Set global knit options
opts_knit$set(
	# Set working dir as project root dir
	root.dir = rprojroot::find_rstudio_root_file()
)

# Set working dir for setup chunk
setwd(rprojroot::find_rstudio_root_file())
getwd()

# Make results dir
results_dir = paste0(params$output_dir, "/results", as.character(format(Sys.time(), '--%Y-%m-%d-%H%M%S')), "/")
dir.create(results_dir)
opts_chunk$set(dev = "pdf", fig.path = paste0(results_dir, "figures-Rmd/"))

# Set global chunk options
opts_chunk$set(
	tidy.opts = list(width.cutoff = 60), 
	tidy = TRUE, 
	fig.path = "figures/"
)
```

# Load data

## Read in list of file UUIDs

Using the GDC manifest used to download the files, read in the manifest file as a table

```{r load manifest}
gdc_manifest = read_tsv(params$gdc_manifest_file)
glimpse(gdc_manifest)
head(gdc_manifest)
```

Extract just the GDC file UUIDs

```{r get uuids}
file_uuids = as_tibble(gdc_manifest$id)
glimpse(file_uuids)
head(file_uuids)
```

# Get TCGA case IDs for a list of file UUIDs using `GenomicDataCommons` package

## Write function to translate list of UUIDs to GDC submitter IDs (i.e. case IDs / TCGA barcodes)

Define function

```{r}
TCGAtranslateID <- function(file_ids, legacy = FALSE) {
	info = files(legacy = legacy) %>% 
		filter(~ file_id %in% file_ids) %>% 
		select('cases.samples.submitter_id') %>% 
		results_all()
	# The mess of code below is to extract TCGA barcodes
    # id_list will contain a list (one item for each file_id)
    # of TCGA barcodes of the form 'TCGA-XX-YYYY-ZZZ'
    id_list = lapply(info$cases,function(a) {
        a[[1]][[1]][[1]]})
    # so we can later expand to a data.frame of the right size
    barcodes_per_file = sapply(id_list,length)
    # And build the data.frame
    return(data.frame(file_id = rep(ids(info),barcodes_per_file),
                      submitter_id = unlist(id_list)))
}
```

## Translate `file_uuids`

Get case/submitter ID from input list of file UUIDs

```{r}
res = TCGAtranslateID(file_uuids)
head(res)
```

Save [UUID <-> case ID] translation table

```{r write ID conversion table}
# TODO: remove trailing 'gdc_manifest' part of filename
write_tsv(x = res, path = paste0(results_dir, tools::file_path_sans_ext(basename(params$gdc_manifest_file)), "-UUID-caseID-table.tsv"))
```
