---
title: 'Clustering of Mutation Signature Analysis Results for Multiple Species'
author: 'Leo Williams'
date: |
  | Created: 2020 01_Jan 30
  | Updated: `r format(Sys.time(), "%Y %m_%b %d")`
params:
  # REQUIRED ----------------------------------------
  in_info_table_multispecies: ''
  in_multisp_mut_mat: ''
  out_dir: ''
  cosmic_signatures: '/Volumes/Pursell-Lab-HD/Pursell-lab/projects/project_02--DNA-seq-analysis/02--data/02--reference-data/COMIC-mutation-signatures/COSMIC-mutation-signatures-v3-no-artif-formatted.csv'
  denovo_sigs_to_extract: 5
  number_of_contrib_muts_to_select: 10
  # OPTIONAL ----------------------------------------
  out_opt_id: '' # string, empty string, or NULL
  info_table_cluster_categories: !r c(NULL) # vector or null
  info_table_cluster_categories_colors: !r list(NULL) # list or NULL
  pheat_cutree_rows_cosmic: NULL # integer or NULL
  pheat_cutree_rows_denovo: NULL # integer or NULL
  remove_samples: no # yes or no
  list_sample_names_to_remove: NULL' # filepath to newline-separated strings or NULL
---

# About

This script take the resulting combined mutation matrices from multiple species from the previous mutation signatures analysis script, combines them, then clusters in a heatmap all samples, independent of species. This is due to the first part of the mutational signatures analysis script referencing the genome, which does not work over multiple species.

# Setup

```{r setup}

# 1. load packages ----
library(knitr)
library(NMF)
library(MutationalPatterns)
library(gridExtra)
library(pheatmap)
library(tidyverse)

# 2. set global knit options ----
opts_knit$set(
    # set project root dir as working dir
    root.dir = rprojroot::find_rstudio_root_file()
)

# 3. Set working dir for setup chunk ----
setwd(rprojroot::find_rstudio_root_file())
getwd()

# 4. Make results dir ----
if (!is.null(params[["out_opt_id"]])) {
    dir_results = paste0(params$out_dir,
                         "/results",
                         as.character(format(Sys.time(),
                                             '--%Y-%m-%d-%H%M%S')),
                         "--",
                         params$out_opt_id)
    dir.create(dir_results)
} else {
    dir_results = paste0(params$out_dir,
                         "/results",
                         as.character(format(Sys.time(),
                                             '--%Y-%m-%d-%H%M%S')))
    dir.create(dir_results)
}

# * 4.1. make results subdirectories ----
dir_results_data = paste0(dir_results, "/data")
dir.create(dir_results_data)
dir_results_tables = paste0(dir_results, "/tables")
dir.create(dir_results_tables)
dir_results_plots = paste0(dir_results, "/plots")
dir.create(dir_results_plots)

# dir_tmp = paste0(dir_results, "/tmp")
# dir.create(dir_tmp)

# 5. get filepath of current script to copy into results dir ----
src_filepath = rstudioapi::getSourceEditorContext()$path
file.copy(from = src_filepath, to = dir_results)

# # 6. Export shell environment variables ----
# Sys.setenv(
# 	# results dirs and subdirs
# 	dir_results = dir_results, 
# 	dir_results_plots = dir_results_plots, 
# 	dir_results_tables = dir_results_tables, 
# 	# tmp dir
# 	dir_tmp = dir_tmp,
# 	# filepath of current script
# 	src_filepath = src_filepath
# )
# 
# # 7. Set global chunk options ----
# opts_chunk$set(
# 	tidy.opts = list(width.cutoff = 60),
# 	tidy = TRUE,
# 	dev = "pdf",
# 	fig.path = paste0(dir_results, "/figures-Rmd/")
# )
# 
# # 8. set ggplot theme ----
# theme_set(theme_classic() +
#           theme(panel.grid.major = element_line(colour = "#DDDDDD"),
#                 panel.grid.minor = element_line(color = "#FFFFFF"),
#                 text = element_text(size = 16, face = "bold")))
```

# Load Input Data

Load combined human/mouse input sample info table:

```{r load input table}
in_info_table_multisp <- read_tsv(params$in_info_table_multisp,
                                  col_types = cols(
                                      individual = col_factor(),
                                      is_tumor = col_factor(),
                                      `is_pre-recombination_normal` = col_factor()
                                  ))
in_info_table_multisp
```

If samples to be removed, load list of sample names to be removed:
```{r load sample names to remove}
if (params$remove_samples == TRUE) {
    tSampleNamesRm = read_tsv(file = params$list_sample_names_to_remove, col_names = "sample_name_rm")
    # tSampleNamesRm = tSampleNamesRm[[1]]
    tSampleNamesRm
}
```

Remove samples from info table if indicated:
```{r remove samples}
if (params$remove_samples == TRUE) {
    in_info_table_multisp = in_info_table_multisp %>%
        filter(!(sample_name %in% tSampleNamesRm[["sample_name_rm"]]))
    in_info_table_multisp
}
```

Remove samples from

Assign pheatmap annotations:

```{r assign pheatmap annotations}
# from input info table, define categorical annotations for plotting on pheatmaps
# define categorical annotations
if (exists("info_table_cluster_categories", where = params)) {
annotations = data.frame(
    in_info_table_multisp[,params$info_table_cluster_categories], 
    row.names = in_info_table_multisp$sample_name
    )
}
```

Load combined human/mouse mutation matrix and remove samples if indicated by params:

```{r load human contrib table}
tib_mut_mat_multisp <- read_tsv(params$in_multisp_mut_mat)

# remove samples if indicated
if (params$remove_samples == TRUE) {
    tib_mut_mat_multisp = tib_mut_mat_multisp %>%
        # select trinuc header col, then only select sample cols NOT in the list of excluded sample names
        select(`trinucleotide context`, !(matches(tSampleNamesRm[["sample_name_rm"]])))
}

# transform tibble to matrix format as needed by MutationalPatterns and NMF. Dont include trinuc context - add as rownames after
mut_mat_multisp = as.matrix(tib_mut_mat_multisp[, -1])

# add trinuc contexts as matrix rownames
rownames(mut_mat_multisp) = tib_mut_mat_multisp[[1]]

# print 5x5 sample of complete matrix
mut_mat_multisp[1:5, 1:5]
```

# Analysis

<!-- ## Transform input tables -->

<!-- Convert input mutation signature contribution tibble/data frame back into a matrix: -->

<!-- ```{r convert mut sig contrib back to matrix} -->
<!-- combined_sig_contrib_mat <- in_multisp_mut_mat %>%  -->
<!--     select(-sample_name) %>% -->
<!--     as.matrix() -->

<!-- rownames(combined_sig_contrib_mat) = in_multisp_mut_mat[["sample_name"]] -->
<!-- ``` -->

## De Novo Mutation Signatures

Add a small pesudocount to the mutation count matrix

```{r psudocount}
mut_mat_multisp = mut_mat_multisp + 0.001
```

From "An introduction to NMF package" (Gaujoux 2018):

> A critical parameter in NMF is the factorization rank r. It deﬁnes the number of metagenes used to approximate the target matrix. Given a NMF method and the target matrix, a common way of deciding on r is to try diﬀerent values, compute some quality measure of the results, and choose the best value according to this quality criteria.

> Several approaches have then been proposed to choose the optimal value of r. For example, (Brunet 2004) proposed to ***take the ﬁrst value of r for which the cophenetic coefficient starts decreasing,*** (Hutchins 2008) suggested to ***choose the ﬁrst value where the RSS curve presents an inﬂection point***, and (Frigyesi 2008) considered ***the smallest value at which the decrease in the RSS is lower than the decrease of the RSS obtained from random data***.

> When the seeding method is stochastic, multiple runs are usually required to achieve stability or a resonable result. This can be done by setting argument nrun to the desired value. For performance reason we use nrun=5 here, but a typical choice would lies between 100 and 200:

Use the NMF package to generate an estimate rank plot:

```{r estimate nmf rank}
estimate = nmf(mut_mat_multisp,
               rank = 2:ncol(mut_mat_multisp),
               method = "brunet",
               nrun = 10,
               seed = 123456) # default
```

Plot the NMF estimate:

```{r plot nmf est}
plot(estimate)
# save fig
ggsave(filename = paste0(dir_results_plots, "/01--NMF-rank-estimate.pdf"), height = 10, width = 20)
```

Extract signatures based on the chosen factorization rank according to results from the NMF rank survey:

```{r sig extract NMF}
# TODO: automatically analyze the best rank by analyzing the values in 'estimate' e.g. when cophenetic begins to drop ||OR|| split script into pre-NMF and post-NMF to allow for changing extraction rank based on intermediate results of NMF estimate?
# Extract signatures based on qualitative analysis of rank estimate
# FIXME: generalize rank selection based on the previous estimate
de_novo_nmf_res = extract_signatures(mut_mat_multisp, rank = params$denovo_sigs_to_extract, nrun = 10)
```

Plot the 96 trinucleotide distributions of the de novo mutation signatures:

```{r plot nmf sigs}
ymax_nmf_plot = max(de_novo_nmf_res$signatures / colSums(de_novo_nmf_res$signatures))
plot_96_profile(de_novo_nmf_res$signatures,
                # ymax = ymax_nmf_plot + (0.2*ymax_nmf_plot))
                ymax = round(ymax_nmf_plot + 0.05, digits = 1))

# save fig
ggsave(filename = paste0(dir_results_plots, "/02--de-novo-NMF-sigs.pdf"),
       height = (1.2*ncol(de_novo_nmf_res$signatures)),
       width = 12)
```

Plot the de novo signature contributions in a bar plot:

```{r}
    pc1 = plot_contribution(de_novo_nmf_res$contribution,
                        de_novo_nmf_res$signature,
                        mode = "relative") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
pc1
# save fig
ggsave(filename = paste0(dir_results_plots, "/03--de-novo-NMF-sigs-rel-contrib.pdf"),
       height = 12,
       width = (8+ 0.2 * ncol(de_novo_nmf_res$contribution)),
       limitsize = F)

# Plot absolute contribution
pc2 = plot_contribution(de_novo_nmf_res$contribution,
                        de_novo_nmf_res$signature,
                        mode = "absolute") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab("Absolute contribution (no. of mutations)")
pc2
# save fig
ggsave(filename = paste0(dir_results_plots, "/04--de-novo-NMF-sigs-abs-contrib.pdf"),
       height = 12,
       width = (8 + 0.2 * ncol(de_novo_nmf_res$contribution)),
       limitsize = F)

# Combine both plots
grid.arrange(pc1, pc2)
# save fig
pdf(file = paste0(dir_results_plots, "/05--de-novo-NMF-sigs-rel-abs-contribs.pdf"),
    height = 12,
    width = (8 + 0.2 * ncol(de_novo_nmf_res$contribution)))
grid.arrange(pc1, pc2)
dev.off()
```

Plot heatmap of sample de novo signature contribution with hierarchical clustering and labeled metadata:

```{r plot de novo heatmap}
nmf_res_contrib = as_tibble(de_novo_nmf_res$contribution,
							rownames = NA)
# View(nmf_res_contrib)
nmf_res_contrib = t(nmf_res_contrib)
nmf_res_contrib_norm = nmf_res_contrib/rowSums(nmf_res_contrib)
colnames(nmf_res_contrib_norm) = as.character(1:ncol(nmf_res_contrib_norm))
# View(nmf_res_contrib_norm)

# ADAPTED FROM COSMIC HEATMAP ---
# save plot (must save before plotting inline for pheatmap)
# open pdf device
pdf(file = paste0(dir_results_plots, "/06--de-novo-NMF-sig-contrib-heatmap.pdf"),
    width = (3 + (1 * ncol(nmf_res_contrib_norm))),
    height = (2 + (0.2 * nrow(nmf_res_contrib_norm)) + (0.2 * length(params$info_table_cluster_categories_colors))))
# render heatmap
pheatmap(mat = nmf_res_contrib_norm,
         cluster_rows = T, cluster_cols = F,
         clustering_method = "complete",
         annotation_row = if (exists("annotations")) annotations else NA,
         annotation_colors = if (exists("info_table_cluster_categories", where = params)) params$info_table_cluster_categories_colors else NA,
         cutree_rows = if ((exists("pheat_cutree_rows_denovo", where = params))) params$pheat_cutree_rows_denovo else NA,
         treeheight_row = 100,
         main = "Hierarchical Clustering by de novo NMF Mutation Signature Contribution",
         angle_col = 90, display_numbers = F)
# turn off pdf device
dev.off()

# plot inline
# FIXME: When inline plot is plotted first and then PDF plots are subsequently saved, the first saved PDF plot is corrupted
pheatmap(mat = nmf_res_contrib_norm,
         cluster_rows = T, cluster_cols = F,
         clustering_method = "complete",
         annotation_row = if (exists("annotations")) annotations else NA,
         annotation_colors = if (exists("info_table_cluster_categories", where = params)) params$info_table_cluster_categories_colors else NA,
         cutree_rows = if ((exists("pheat_cutree_rows_denovo", where = params))) params$pheat_cutree_rows_denovo else NA,
         treeheight_row = 100,
         main = "Hierarchical Clustering by de novo NMF Mutation Signature Contribution",
         angle_col = 90, display_numbers = F)
```

Compare the reconstructed mutational profile with the original profile of the first sample

```{r}
# for a single sample
plot_compare_profiles(mut_mat_multisp[,1],
                      de_novo_nmf_res$reconstructed[,1],
                      profile_names = c("Original", "Reconstructed"))
# save fig
ggsave(filename = paste0(dir_results_plots, "/07--denovo-reconstruct-1Sample.pdf"),
       width = 8,
       height = 6)
```

Calculate cosine similarity between all original and reconstructed mutational profile with `cos_sim_matrix`:

```{r calc de novo cos sim}
# Calculate all pairwise cosine similarities
cos_sim_denovo_ori_rec = cos_sim_matrix(mut_mat_multisp, de_novo_nmf_res$reconstructed)

# Extract cosine similarities per sample between original and reconstructed
cos_sim_denovo_ori_rec = as.data.frame(diag(cos_sim_denovo_ori_rec))

# Adjust data frame for plotting with ggplot
colnames(cos_sim_denovo_ori_rec) = "cos_sim"
cos_sim_denovo_ori_rec$sample = row.names(cos_sim_denovo_ori_rec)

# Summary stats on cos_sim
summary(cos_sim_denovo_ori_rec$cos_sim)
```

Plot the cosine similarities between original and reconstructed sample profiles"

```{r plot de novo cos sim}
# Make barplot
ggplot(cos_sim_denovo_ori_rec, aes(x = sample, y = cos_sim)) +
  geom_bar(stat = "identity") +
  # coord_cartesian(ylim=c(0.8,1)) +
  # coord_flip(ylim=c(0.8,1)) +
  ylab("Cosine similarity — De Novo Signatures\n Original vs. Reconstructed") +
  xlab("") +
  # reverse order of the samples such that first is up
  # xlim(rev(levels(factor(cos_sim_ori_rec$sample)))) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
		axis.text.x = element_text(hjust = 1, angle = 90)) +
  # add cut off line
  geom_hline(aes(yintercept=.95))
# Save plot
ggsave(filename = paste0(dir_results_plots, "/08--denovo-cos-sim.pdf"),
       height = 6,
       width = (6 + (.1 * nrow(cos_sim_denovo_ori_rec))),
       limitsize = F)
```

## COSMIC Mutation Signatures

Download the [COSMIC v3 mutation signatures](https://cancer.sanger.ac.uk/cosmic/signatures/SBS/) in table format and reformat them to the format `MutationalPatterns` uses in the introductory guide when describing how to download the COSMIC v2 signatures data table.

Load either the full COSMICv3 signatures or a subset that excludes purported artifactual signatures

```{r load COSMIC signatures}
# Old - for COSMICv2:
# Download mutational signatures from COSMIC website:
# sp_url = paste("https://cancer.sanger.ac.uk/cancergenome/assets/",
#                "signatures_probabilities.txt",
#                sep = "")
# cosmicv3_sigs_no_arts = read.table(sp_url, sep = "\t", header = T)

# Read in COSMICv3 sigs table
cancer_signatures = read.csv(params$cosmic_signatures, header = T)

# Match order of mutation types to MutationalPatterns standard
new_order = match(row.names(mut_mat_multisp), cancer_signatures$Somatic.Mutation.Type)

# Reorder cancer signatures dataframe
cancer_signatures = cancer_signatures[as.vector(new_order),]

# Add trinucleotide changes as row.names
row.names(cancer_signatures) = cancer_signatures$Somatic.Mutation.Type

# Keep only 96 contributions of the signatures in the matrix
cancer_signatures = as.matrix(cancer_signatures[,4:52])

cancer_signatures[1:6, 1:6]
```

Fit mutation matrix to COSMIC signatures:

```{r fir mut mat to cosmic sigs}
fit_res = fit_to_signatures(mut_mat_multisp, cancer_signatures)
```

Plot the optimal contribution of the COSMIC signatures in each sample as a stacked barplot:

```{r plot cosmic sig contrib rowsums}
# calculate distribution of how many mutations each signature contributes across all samples
contribution_rowsums = tibble(signature = factor(rownames(fit_res$contribution),
                                                 levels = rownames(fit_res$contribution)),
                              total_contribution = rowSums(fit_res$contribution))

# plot barplot
ggplot(contribution_rowsums, aes(x = signature, y = total_contribution)) +
    geom_col() +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
# save plot
ggsave(filename = paste0(dir_results_plots, "/09--total-mut-contrib-by-COSMIC-sig.pdf"),
       height = 6,
       width = 8)

# Select sigs that contribute more than 10 mutations across all samples
# TODO: add param to select signatures based on either 1) total muts contributed across all samples, or 2) % muts contributed across all samples
select = which(rowSums(fit_res$contribution) > params$number_of_contrib_muts_to_select)
# show all rows (signatures) that were selected
rownames(fit_res$contribution[select,])
# other selection criteria based on Temko 2019 [@2018TemkoSomaticPOLEexonuclease]: only select signatures that contribute a certain % of the total mutations across samples
select_pct = which(rowSums(fit_res$contribution) >=
                (0.01 * sum(rowSums(fit_res$contribution))))
rownames(fit_res$contribution[select_pct,])
```

Plot COSMIC signature contributions for each sample:

```{r plot cosmic sig contrib}
# plot relative contribution barplot
pc3 = plot_contribution(fit_res$contribution[select,],
                  cancer_signatures[,select],
                  # mode = "relative")
                  mode = "relative") +
	theme(axis.text.x = element_text(angle = 90, hjust = 1))
pc3
# save fig
ggsave(filename = paste0(dir_results_plots, "/10--COSMIC-contrib-rel.pdf"),
       width = 4 + 0.2 * ncol(fit_res$contribution[select,]),
       height = 12,
       limitsize = F)

# Plot absolute contribution barplot
pc4 = plot_contribution(fit_res$contribution[select,],
                        cancer_signatures[,select],
                        mode = "absolute") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
pc4
# save fig
ggsave(filename = paste0(dir_results_plots, "/11--COSMIC-contrib-abs.pdf"),
       width = 4 + 0.2 * ncol(fit_res$contribution[select,]),
       height = 12,
       limitsize = F)
```

Normalize COSMIC signature contribution according to internal workings of the `plot_contribution_heatmap()` function in `MutationalPatterns` and export for reproducibility:

```{r normalize cosmic sig contrib and export}
# normalize COSMIC sigs contribution (adapted from plot_contribution_heatmap() function)
cosmic_res_contrib = as_tibble(fit_res$contribution,
                               rownames = NA)
cosmic_res_contrib = t(cosmic_res_contrib)
cosmic_res_contrib_norm = cosmic_res_contrib/rowSums(cosmic_res_contrib)
# export to .tsv
write_tsv(x = as_tibble(cosmic_res_contrib_norm, rownames = "sample_name"),
          path = paste0(dir_results_tables, "/01--cosmic-contrib-norm.tsv"))
```

Plot COSMIC signature contribution heatmap with hierarchical clustering based on combined signatured contribution similarity, and sample metadata categorical labels:

```{r plot cosmic sig contrib heatmap}
# save plot 1
pdf(file = paste0(dir_results_plots, "/12--heatmap-COSMIC-contrib.pdf"),
    width = 12,
    height = 3 + (0.1 * nrow(cosmic_res_contrib_norm)) + (0.25 * length(params$info_table_cluster_categories_colors)))
pheatmap(mat = cosmic_res_contrib_norm,
		 cluster_rows = T, cluster_cols = F,
		 clustering_method = "complete",
		 annotation_row = if (exists("annotations")) annotations else NA,
		 annotation_colors = if (exists("info_table_cluster_categories_colors", where = params)) params$info_table_cluster_categories_colors else NA,
		 cutree_rows = if ((exists("pheat_cutree_rows_cosmic", where = params))) params$pheat_cutree_rows_cosmic else NA,
		 treeheight_row = 100,
		 main = "COSMIC Mutation Signature Contribution & Sample Clustering",
		 angle_col = 90, display_numbers = F)
dev.off()

# plot inline
# FIXME: When inline plot is plotted first and then PDF plots are subsequently saved, the first saved PDF plot is corrupted
pheatmap(mat = cosmic_res_contrib_norm,
		 cluster_rows = T, cluster_cols = F,
		 clustering_method = "complete",
		 annotation_row = if (exists("annotations")) annotations else NA,
		 annotation_colors = if (exists("info_table_cluster_categories_colors", where = params)) params$info_table_cluster_categories_colors else NA,
		 cutree_rows = if ((exists("pheat_cutree_rows_cosmic", where = params))) params$pheat_cutree_rows_cosmic else NA,
		 treeheight_row = 100,
		 main = "COSMIC Mutation Signature Contribution & Sample Clustering",
		 angle_col = 90, display_numbers = F)
```
Plot same heatmap except display numbers inside cells:
```{r plot cosmic sig contrib heatmap nums}
# save plot 1
pdf(file = paste0(dir_results_plots, "/13--heatmap-COSMIC-contrib-w-nums.pdf"),
    width = 20,
    height = 4 + (0.1 * nrow(cosmic_res_contrib_norm)) + (0.25 * length(params$info_table_cluster_categories_colors)))
pheatmap(mat = cosmic_res_contrib_norm,
		 cluster_rows = T, cluster_cols = F,
		 clustering_method = "complete",
		 annotation_row = if (exists("annotations")) annotations else NA,
		 annotation_colors = if (exists("info_table_cluster_categories_colors", where = params)) params$info_table_cluster_categories_colors else NA,
		 cutree_rows = if ((exists("pheat_cutree_rows_cosmic", where = params))) params$pheat_cutree_rows_cosmic else NA,
		 treeheight_row = 100,
		 main = "COSMIC Mutation Signature Contribution & Sample Clustering",
		 angle_col = 90, display_numbers = T)
dev.off()

# plot inline
# FIXME: When inline plot is plotted first and then PDF plots are subsequently saved, the first saved PDF plot is corrupted
pheatmap(mat = cosmic_res_contrib_norm,
		 cluster_rows = T, cluster_cols = F,
		 clustering_method = "complete",
		 annotation_row = if (exists("annotations")) annotations else NA,
		 annotation_colors = if (exists("info_table_cluster_categories_colors", where = params)) params$info_table_cluster_categories_colors else NA,
		 cutree_rows = if ((exists("pheat_cutree_rows_cosmic", where = params))) params$pheat_cutree_rows_cosmic else NA,
		 treeheight_row = 100,
		 main = "COSMIC Mutation Signature Contribution & Sample Clustering",
		 angle_col = 90, display_numbers = T)
```

<!-- TODO: plot specified COSMIC sigs of interest for easy reference? -->

<!-- TODO: add calculation of per-sample cosine similarity to COSMIC sigs? -->


<!-- ## Plot cluster heatmap -->

<!-- Plot heatmap with clustering based on signature contribution similarity -->

<!-- ```{r plot COSMIC mutation signature contribution heatmap 1} -->
<!-- # save plot -->
<!-- pdf(file = paste0(results_dir, "/19.01--pheat-cosmic-contrib.pdf"),  -->
<!--     width = 12, -->
<!--     height = 6 + 0.1 * nrow(combined_sig_contrib_mat)) -->

<!-- pheatmap(mat = combined_sig_contrib_mat,  -->
<!--          cluster_rows = T, cluster_cols = F,  -->
<!--          clustering_method = "complete",  -->
<!-- 		 annotation_row = if (exists("annotations")) annotations else NA,  -->
<!-- 		 annotation_colors = if (exists("info_table_cluster_categories_colors", where = params)) params$info_table_cluster_categories_colors else NA, -->
<!-- 		 treeheight_row = 100,  -->
<!-- 		 main = "COSMIC Mutation Signature Contribution & Sample Clustering",  -->
<!-- 		 angle_col = 90, display_numbers = F -->
<!-- 		 ) -->
<!-- 		 # cutree_rows = if ((exists("pheat_cutree_rows", where = params))) params$pheat_cutree_rows else NA,  -->
<!-- dev.off() -->

<!-- # plot inline -->
<!-- pheatmap(mat = combined_sig_contrib_mat,  -->
<!--          cluster_rows = T, cluster_cols = F,  -->
<!--          clustering_method = "complete",  -->
<!-- 		 annotation_row = if (exists("annotations")) annotations else NA,  -->
<!-- 		 annotation_colors = if (exists("info_table_cluster_categories_colors", where = params)) params$info_table_cluster_categories_colors else NA, -->
<!-- 		 treeheight_row = 100,  -->
<!-- 		 main = "COSMIC Mutation Signature Contribution & Sample Clustering",  -->
<!-- 		 angle_col = 90, display_numbers = F -->
<!-- 		 ) -->
<!-- 		 # cutree_rows = if ((exists("pheat_cutree_rows", where = params))) params$pheat_cutree_rows else NA,  -->
<!-- ``` -->

# Save Image

Save all current session data to a file in the results folder. You can load this file back and inspect any analyses using the actual data that was produced.

```{r}
save.image(file = paste0(dir_results, "/env-data.RData"))
```

# Session Information

```{r env, comment=NA}
write_lines(capture.output(sessionInfo()), path = paste0(dir_results, "/env-info.txt"))
```

