---
title: 'GDC Data Retrieval from TCGA Case IDs'
author: 'Leo Williams'
date: |
  | 'Created 2020-01-10'
  | 'Updated `r format(Sys.time(), "%Y-%m-%d")`'
params:
  # default
  input_info_table: '/Volumes/Pursell-Lab-HD/Pursell-lab/projects/project_02--DNA-seq-analysis/04--analysis/expt_00--obtain-and-format-data/Vivian-TCGA-hypermut-POLE-pol-muts/00--input/TCGA-POLE-hypermut-pol-domain-mut-case-IDs.tsv'
  output_dir: '/Volumes/Pursell-Lab-HD/Pursell-lab/projects/project_02--DNA-seq-analysis/04--analysis/expt_00--obtain-and-format-data/Vivian-TCGA-hypermut-POLE-pol-muts'
  gdc_token_file: '/Volumes/Pursell-Lab-HD/Pursell-lab/projects/project_02--DNA-seq-analysis/04--analysis/expt_00--obtain-and-format-data/Vivian-TCGA-hypermut-POLE-pol-muts/00--input/gdc-user-token.2020-01-10T20_22_55.971Z.txt'
  optional_output_id: NULL
output:
  html_notebook:
    toc: yes
    toc_float: yes
    number_sections: yes
  pdf_document:
    toc: yes
    number_sections: yes
---

# About

This script takes a list of TCGA case IDs as input and downloads the annotated Varscan2 VCF files

## I/O

Inputs:

- input table of newlin-separated TCGA case IDs

Outputs:

- 
 
# Usage

# Setup

Load packages, set project root/working dir, make results dir, set global chunk options, and set knitr figure output path:

```{r setup, results='hide'}
# load packages
library(knitr)
library(tidyverse)
library(GenomicDataCommons)

# set global knit options
opts_knit$set(
	# Set working dir as project root dir
	root.dir = rprojroot::find_rstudio_root_file()
)

# Set working dir for setup chunk
setwd(rprojroot::find_rstudio_root_file())
getwd()

# Make results dir
if (!is.null(params[["optional_output_id"]])) {
    optional_output_id = params$optional_output_id
results_dir = paste0(params$output_dir, 
                     "/results", 
                     "--", 
                     optional_output_id, 
                     as.character(format(Sys.time(), 
                                         '--%Y-%m-%d-%H%M%S')), 
                     "/") # TODO: go through and properly format dir and file names. i.e. remove all trailing '/' from dir names and add '/' to beginning of file name when defining. this is to conform to standard format of copying dirnames from the terminal because they dont end with a '/'.
dir.create(results_dir)
} else {
results_dir = paste0(params$output_dir, 
                     "/results", 
                     as.character(format(Sys.time(),
                                         '--%Y-%m-%d-%H%M%S')), 
                     "/")
dir.create(results_dir)
}

# set path for knitr figure output
opts_chunk$set(dev = "pdf", fig.path = paste0(results_dir, "figures-Rmd/"))

# Set global chunk options
opts_chunk$set(
	tidy.opts = list(width.cutoff = 60), 
	tidy = TRUE, 
	fig.path = paste0(results_dir, "figures-Rmd/")
)
```

Load TCGA case IDs:

```{r load case IDs}
# Load TCGA case IDs from input table ----
input_info_table = read_tsv(file = params$input_info_table)
                            #, col_types = cols(.default = "c"))
# View(input_info_table)
glimpse(input_info_table)
```

Load and set GDC controlled access token:

```{r load GDC token}
# set GDC token as env variable so it can be read by `gdc_token()`
Sys.setenv(GDC_TOKEN_FILE = params$gdc_token_file)
# set token as local variable
gdc_token <- gdc_token()
```

Check GDC network:

```{r}
status()
stopifnot(status()$status == "OK")
```

# Analysis

## Create query

1. Create a files query:

```{r make files query}
fquery <- files()
# inspect GDfquery object and its default fields
fquery
```

2. Select fields of interest to query:

```{r select fields}
# list available fileds for a 'cases' query
length(available_fields("cases"))
# available_fields("cases")

# select fields of interest:
fquery %>% 
    select()
```

3. Filter field values to limit results:

```{r filter query results}
# without filters, returns all default results:
count(fquery)

# 
```

4. Retrieve results:

```{r retrieve query results}
# NOTE: Don't run `results_all()` unless you have filtered otherwise it could be huge and take a long time!
cresults <- fquery %>% results_all()
cresults
```

