---
title: 'Get metadata for GDC VCFs and move to working directory'
author: 'Leo Williams'
date: |
  | Created: 2020 10_Oct 16
  | Updated: `r format(Sys.time(), "%Y %m_%b %d")`
# output: 
#   html_notebook: 
#     toc: yes
#     toc_float: yes
params:
  # REQUIRED ########################################
  in_dir: '/Volumes/Pursell-Lab-HD/Pursell-lab/01--raw-data/02--external/NIH-GDC/POLE-related/2020-10-06--TCGA-all-CRC-UCEC/download' # string ; path to dir hierarchy containing GDC VCF files
  out_dir: '/Volumes/Pursell-Lab-HD/Pursell-lab/01--raw-data/02--external/NIH-GDC/POLE-related/2020-10-06--TCGA-all-CRC-UCEC' # string ; path to dir where results dir will be made
  copy_and_rename_working_files: no # boolean ; default=no ; whether or not VCF files should be renamed based on TCGA case ID and workflow and moved to a working directory for further analysis.
  out_dir_working: '' # string ; path to working dir where renamed VCF files will be copied to
  # OPTIONAL ########################################
  out_opt_id: NULL # [NULL|string] ; default=NULL ; optional tag to append to name of results dir
---

# About

This script takes as input a directory which a hierarchy that contains VCF files downloaded from the GDC using the `gdc-client download` tool, queries the GDC for metadata associated with the files, and copies and renames the VCFs to a working directory if indicated. The VCFs should have the files' UUIDs as the file rootnames as originally downloaded from the GDC.

# Setup

```{r setup, message=FALSE}
# Load packages ----
library(knitr)
library(extrafont)
library(RColorBrewer)
library(tidyverse)

# Set global knit options ----
opts_knit$set(
    # set project root dir as working dir
    root.dir = rprojroot::find_rstudio_root_file()
)

# Set working dir for setup chunk ----
setwd(rprojroot::find_rstudio_root_file())
getwd()

# Set global chunk options ----
# opts_chunk$set(
# 	tidy.opts = list(width.cutoff = 60),
# 	tidy = TRUE,
# 	dev = "pdf",
# 	fig.path = paste0(dir_results, "/figures-Rmd/")
# )
```

```{r other setup}
# make results dir ----
if (!is.null(params[["out_opt_id"]])) {
	# set results dir name
    dir_results = paste0(
    	params$out_dir,
    	"/results-GDC-metadata",
    	as.character(format(Sys.time(),
    						'--%Y-%m-%d-%H%M%S')),
    	if (exists("out_optID", where = params)) {
    		paste0("--",params$out_optID)
    	}
    )

    # make results dir
    dir.create(dir_results)
} else {
	# set simple results dir name
    dir_results = paste0(params$out_dir,
                         "/results",
                         as.character(format(Sys.time(),
                                             '--%Y-%m-%d-%H%M%S')))
    # create results dir
    dir.create(dir_results)
}

# make results subdirs ----
# dir_results_data = paste0(dir_results, "/data")
# dir.create(dir_results_data)
# dir_results_tables = paste0(dir_results, "/tables")
# dir.create(dir_results_tables)
# dir_results_plots = paste0(dir_results, "/plots")
# dir.create(dir_results_plots)
# dir_tmp = paste0(dir_results, "/tmp")
# dir.create(dir_tmp)

# export current script to results dir for reproducibility ----
src_filepath = rstudioapi::getSourceEditorContext()$path
file.copy(from = src_filepath, to = dir_results)

# export variables to shell environment ----
Sys.setenv(
	# results dirs and subdirs
	dir_results = dir_results,
	# filepath of current script
	src_filepath = src_filepath
)
```

# Load Data

# Transform Data

## Get VCF [file\|base\|root]names

```{bash}

```

# Analyze Data

# Session Info

```{r save session data}
# save data image
save.image(file = paste0(dir_results, "/data.Rdata"))

# save session info
write_lines(capture.output(sessionInfo()), 
            path = paste0(dir_results, "/sessionInfo.txt"))
```
