---
title: 'Get GDC VCF UUIDs, Case IDs, and Join with File/Base/Rootname Table'
author: 'Leo Williams'
date: |
  | Created: 2020 May 09
  | Updated: `r format(Sys.time(), "%Y %m_%b %d")`
params:
  in_dirh_gdc_download_vcfs: '' # string: path to dir
  out_dir: '' # string: path to dir
  out_opt_id: NULL # string or NULL: optional text to include in results dir name
  in_filebaserootname_table: ''
---

# About

This script takes a dir of VCFs obtained from the Genomic Data Commons (GDC) and outputs a table with the VCF filename, the VCF UUID (which should be the basename of the VCF file), and matching GDC metadata for each GDC VCF file like TCGA case ID.

# Setup

```{r setup}
# Load packages ----
library(knitr)
library(tidyverse)
library(GenomicDataCommons)

# Set global knit options ----
opts_knit$set(
    # set project root dir as working dir
    root.dir = rprojroot::find_rstudio_root_file()
)

# Set working dir for setup chunk ----
setwd(rprojroot::find_rstudio_root_file())
getwd()

# Set global chunk options ----
# opts_chunk$set(
# 	tidy.opts = list(width.cutoff = 60),
# 	tidy = TRUE,
# 	dev = "pdf",
# 	fig.path = paste0(dir_results, "/figures-Rmd/")
# )
```

```{r other setup}
# make results dir ----
if (!is.null(params[["out_opt_id"]])) {
	# set results dir name
    dir_results = paste0(params$out_dir,
                         "/results",
                         as.character(format(Sys.time(),
                                             '--%Y-%m-%d-%H%M%S')),
                         if (exists("out_opt_id", where = params)) {paste0("--", params$out_opt_id)})
    
    # make results dir
    dir.create(dir_results)
} else {
	# set simple results dir name
    dir_results = paste0(params$out_dir,
                         "/results",
                         as.character(format(Sys.time(),
                                             '--%Y-%m-%d-%H%M%S')))
    # create results dir
    dir.create(dir_results)
}

# make results subdirs ----
# dir_results_data = paste0(dir_results, "/data")
# dir.create(dir_results_data)
dir_results_tables = paste0(dir_results, "/tables")
dir.create(dir_results_tables)
# dir_results_plots = paste0(dir_results, "/plots")
# dir.create(dir_results_plots)
# dir_tmp = paste0(dir_results, "/tmp")
# dir.create(dir_tmp)

# export current script to results dir for reproducibility ----
src_filepath = rstudioapi::getSourceEditorContext()$path
file.copy(from = src_filepath, to = dir_results)

# export variables to shell environment ----
Sys.setenv(
	# results dirs and subdirs
	dir_results = dir_results,
	# dir_results_plots = dir_results_plots,
	dir_results_tables = dir_results_tables,
	# tmp dir
	# dir_tmp = dir_tmp,
	# filepath of current script
	src_filepath = src_filepath
)
```

Load parameters as variables

# Load data

```{r get vcf filepaths}
# read input dir of GDC VCFs
in_dir_of_vcfs = params$in_dirh_gdc_download_vcfs
in_dir_of_vcfs

# make vector of absolute filepaths of all VCFs in input dir
vcf_filepaths = dir(path = in_dir_of_vcfs,
                           pattern = ".vcf.gz$",
                           full.names = T,
                           recursive = T)
```

Make a tibble to store all desired VCF info and metadata, and initialize it with the filepaths of the GDC VCFs in the input dir:

```{r make data table}
# make tibble with first column as the VCF filepaths
gdc_data_table = tibble(vcf_filepath = vcf_filepaths)
```

Add a second column to the data table with the VCF file GDC UUIDs, which should be the VCF file basenames:

```{r add UUIDs}
gdc_data_table = gdc_data_table %>%
    mutate(GDC_UUID = str_extract(vcf_filepath, "[:alnum:]{8}-[:alnum:]{4}-[:alnum:]{4}-[:alnum:]{4}-[:alnum:]{12}"))
```

# Get other GDC metadata from GDC VCF UUIDs

Check GDC network status:

```{r check GDC status}
status()
stopifnot(status()$status == "OK")
```

Initialize a GDCquery object with `files()`

```{r make files query}
fquery = files()
fquery
```

View available fields to query:

```{r select files fields}
# list how many fields available
length(available_fields("files"))
# available_fields("files")

# search within available fields
grep_fields(entity = "files", pattern = "tissue")

# select fields of interest

```

Select desired fields to query:

```{r select query fields}
# TODO: add param char vector for additional fields to retrieve in addition to default
# FIXME:
fquery_select = fquery %>%
    select(c(
    	"file_id", 
    	"submitter_id", 
    	"cases.submitter_id", 
    	"cases.case_id", 
    	# "analysis.submitter_id",
    	# "analysis.workflow_type", 
    	"cases.diagnoses.tissue_or_organ_of_origin"
    ))
summary(fquery_select)
```

Filter query fields for desired values:

```{r filter query fields}
fquery_filter = fquery_select %>%
    filter(~ file_id %in% gdc_data_table[["GDC_UUID"]])
summary(fquery_filter)
```

Return all query results:

```{r get query results}
fquery_res = fquery_filter %>%
    results_all()

# show summary of query results
summary(fquery_res)

# glimpse the structure of the GDCquery object
# glimpse(fquery)
```

Iterate through query results and add each section to the data table:

```{r convert query list to a nested df}
# turn GDCquery into a tibble
fquery_tib = as_tibble(fquery_res)
glimpse(fquery_tib)
```

Unnest the converted df that contains lists and other dfs

```{r unnest the df}
# unnest the nested 'cases' fields - 'analysis' fields should have been unnested correctly with the previous conversion to a tibble since they're only 1 level deep
fquery_tib_unnest = fquery_tib %>%
	unnest(cols = cases, names_sep = ".") %>%
	unnest(cols = cases.diagnoses)
	# FIXME: how to properly unnest the nested analysis df
	# unnest(cols = analysis)
glimpse(fquery_tib_unnest)
```

Add broader tissue of origin categories:

```{r condense tissue labels}
# # fquery_tib_condensed = 
# fquery_tib_unnest %>%
# 	mutate(tissue_of_origin = case_when(
# 		str_detect(tissue_or_organ_of_origin, "colon") ~ "colon"
# 	))
```

Output a TCGA case ID:file UUID match table

```{r}
case_id_match_table = fquery_tib_unnest %>%
	dplyr::select(
		cases.submitter_id, 
		# analysis.workflow_type, 
		tissue_or_organ_of_origin,
		file_id, 
		submitter_id, 
		cases.case_id, 
		# analysis.submitter_id
	)
    # dplyr::select(TCGA_case_ID = cases.submitter_id, VCF_UUID = file_id)
glimpse(case_id_match_table)

write_tsv(x = case_id_match_table, path = paste0(dir_results_tables, "/case_id_UUID_table.tsv"))

```

# Join with FileBaseRootname table based on file rootname/GDC UUID

Load file/base/rootname table

```{r}
tab_fbrnames = read_tsv(params$in_filebaserootname_table)
glimpse(tab_fbrnames)
```

Join case ID-UUID table to fbrootnames table:

```{r}
combined_file_and_metadata_table = left_join(keep = T, 
									 x = tab_fbrnames, 
									 y = case_id_match_table, 
									 by = c("file_rootname" = "file_id"))
combined_file_and_metadata_table %>%
		# tissue_or_organ_of_origin, 
		# absolute_filepath, 
		# file_basename, 
		# file_rootname, 
		# file_id, 
		# everything())
glimpse(combined_file_and_metadata_table)
```

save full filebaserootname and matched IDs table as TSV:

```{r}
write_tsv(x = tab_fbrnames_matched_IDs, 
		  path = paste0(dir_results_tables,
		  				"/combined-GDC-metadata-and-file-info.tsv"))
```
