---
title: 'Rename GDC VCFs from UUID to Case ID'
author: 'Leo Williams'
date: |
  | Created: 2020 06_June 24, 7:14 PM CDT
  | Updated: `r format(Sys.time(), "%Y %m_%b %d")`
params:
  in_dir_of_gdc_vcfs: '/Volumes/Pursell-Lab-HD/Pursell-lab/01--raw-data/02--external/NIH-GDC/POLE-related/2020-10-06--TCGA-all-CRC-UCEC/download'
  in_combined_file_and_metadata_table: '/Volumes/Pursell-Lab-HD/Pursell-lab/02--projects/project_02--DNA-seq-analysis/02--data/01--semiraw-data/02--external/GDC/2020-10-06--TCGA-all-CRC-UCEC/02--metadata-merge/results--2020-10-19-113939/tables/combined-GDC-metadata-and-file-info.tsv'
  out_dir: '/Volumes/Pursell-Lab-HD/Pursell-lab/02--projects/project_02--DNA-seq-analysis/02--data/01--semiraw-data/02--external/GDC/2020-10-06--TCGA-all-CRC-UCEC/03--move-and-rename-VCFs'
  out_opt_id: ''
---

# About

This script takes input of a table with full filepath, basename, and rootnames of a set of GDC gzip'd VCFs, as well as columns for matched GDC case IDs to the VCF file UUIDs (the file rootnames). It finds the gzip VCFs, moves them to the working results dir, renames them with the case ID as the file rootname for each file, and unzips them. This makes it easier to plot case IDs as samples in mutation analysis.

# Setup

```{r setup}
# Load packages ----
library(knitr)
library(tidyverse)

# Set global knit options ----
opts_knit$set(
    # set project root dir as working dir
    root.dir = rprojroot::find_rstudio_root_file()
)

# Set working dir for setup chunk ----
setwd(rprojroot::find_rstudio_root_file())
getwd()

# Set global chunk options ----
# opts_chunk$set(
# 	tidy.opts = list(width.cutoff = 60),
# 	tidy = TRUE,
# 	dev = "pdf",
# 	fig.path = paste0(dir_results, "/figures-Rmd/")
# )
```

```{r other setup}
# make results dir ----
if (!is.null(params[["out_opt_id"]])) {
	# set results dir name
    dir_results = paste0(params$out_dir,
                         "/results",
                         as.character(format(Sys.time(),
                                             '--%Y-%m-%d-%H%M%S')),
                         if (exists("out_opt_id", where = params)) {paste0("--", params$out_opt_id)})
    
    # make results dir
    dir.create(dir_results)
} else {
	# set simple results dir name
    dir_results = paste0(params$out_dir,
                         "/results",
                         as.character(format(Sys.time(),
                                             '--%Y-%m-%d-%H%M%S')))
    # create results dir
    dir.create(dir_results)
}

# make results subdirs ----
dir_results_data = paste0(dir_results, "/data")
dir.create(dir_results_data)
dir_results_tables = paste0(dir_results, "/tables")
dir.create(dir_results_tables)
dir_results_plots = paste0(dir_results, "/plots")
dir.create(dir_results_plots)
dir_tmp = paste0(dir_results, "/tmp")
dir.create(dir_tmp)

# export current script to results dir for reproducibility ----
src_filepath = rstudioapi::getSourceEditorContext()$path
file.copy(from = src_filepath, to = dir_results)

# export variables to shell environment ----
Sys.setenv(
	# results dirs and subdirs
	dir_results = dir_results,
	dir_results_data = dir_results_data,
	dir_results_plots = dir_results_plots,
	dir_results_tables = dir_results_tables,
	# tmp dir
	dir_tmp = dir_tmp,
	# filepath of current script
	src_filepath = src_filepath
)
```

# Load Data

Load table of original filebaserootnames and GDC IDs:
```{r load path and id table}
tab_filepaths_metadata = read_tsv(file = params$in_combined_file_and_metadata_table)
glimpse(tab_filepaths_metadata)
```

# Transform Data

## Copy files to working folder

Copy files in `absolute_filepath` column to working results dir

```{r copy files to wd, message=FALSE}
file.copy(from = tab_filepaths_metadata$absolute_filepath, to = dir_results_data)
```

Unzip all `.vcf.gz` files after copying:
```{bash, engine.opts='-l', comment=NA}
echo "Decompressing all '.gz' files in: " "$dir_results_data"

# decompress all .vcf.gz files:
for i in "$dir_results_data"/*.gz
do
  gunzip "$i"
done
```

## Rename VCFs with GDC case ID as file root

Rename the rootname of copied files from the GDC UUID to the GDC case ID

```{r rename files with GDC submitter ID}
# make vector of new files
vec_cp_files_basenames = list.files(path = dir_results_data, pattern = ".+\\.vcf$")

for (ivcf in vec_cp_files_basenames) {
# for (ivcf in "0bcef875-5efa-46f2-95a8-d01a1ccabba9.vep.vcf.gz") { # eg file
  print(paste0("Working on i: ", ivcf)) # e.g. print
  
    # file basename is already the iter
    ivcf_basename = ivcf
    
    # get absolute filepath of file
    ivcf_abs_filepath = paste0(dir_results_data, "/", ivcf_basename)
    print(paste0("Absolute filepath: ", ivcf_abs_filepath))
    
    # get file rootname which is the UUID
    ivcf_rootname = str_extract(string = ivcf_basename, pattern = ".+?(?=\\.)")
    print(paste0("File rootname: ", ivcf_rootname))
    
    # get file extension
    ivcf_ext = str_extract(string = ivcf_basename, pattern = "\\..+")
    print(paste0("File extension: ", ivcf_ext))
    
    # get row number in table for matching rootname to UUID
    match_uuid_rootname_row_no = match(x = ivcf_rootname, table = tab_filepaths_metadata[["file_rootname"]])
    print(paste0("UUID-root match row number: ", match_uuid_rootname_row_no))
    
    # get case ID in same row for the matched row no
    ivcf_case_id = tab_filepaths_metadata[["cases.submitter_id"]][match_uuid_rootname_row_no]
    print(paste0("Matched case ID: ", ivcf_case_id))
    
    # rename VCF file with case ID as file root instead of UUID
    file.rename(from = ivcf_abs_filepath, to = paste0(dir_results_data, "/", ivcf_case_id, ".vep.vcf"))
}
```

# Session Info

```{r save session data}
# save data image
save.image(file = paste0(dir_results, "/data.Rdata"))

# save session info
write_lines(capture.output(sessionInfo()), 
            path = paste0(dir_results, "/sessionInfo.txt"))
```
