---
title: 'Query GDC Metadata with Case IDs'
author: 'Leo Williams'
date: |
  | Created: 2020 Jan 27
  | Updated: '`r format(Sys.time(), "%Y %B %d")`'
params:
  IN_CASE_ID_TSV: 
  OUT_DIR: 
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  pdf_document:
    toc: yes
    number_sections: yes
---

# About

`This script takes as input a TSV of newline-separated GDC case IDs and returns a table of relevant metadata. Currently this metadata is focused on POLE-mutant tumors and variants from the Varscan2 analysis workflow.
` 
## Usage

# Setup

Load packages, make results dir, 
```{r setup}
library(GenomicDataCommons)
library(tidyverse)
```

Sample list of case IDs

```{r case ids}
input_table <- read_tsv(file = params$IN_CASE_ID_TSV)
case_ids = input_table %>% 
    select(GDC_case_ID)
```

Make files query:

```{r files query}
fquery = files()
fquery
```

Select fields:

```{r select fields}
fquery = fquery %>% 
    GenomicDataCommons::select(fields = c("cases.submitter_id", 
                                          "experimental_strategy", 
                                          "analysis.workflow_type"))
fquery
```

Filter fields:

```{r filter fields}
fquery = fquery %>%
    GenomicDataCommons::filter(~ cases.submitter_id %in% case_ids &
                               analysis.workflow_type == "VarScan2 Annotation")
fquery
```

Return response and results:

```{r get response and results}
# return all results
fquery_results = fquery %>% 
    results_all()
fquery_results

fquery_response = fquery %>% 
    response_all()
fquery_response
```

Turn results list into a tibble:

```{r results to tibble}
fquery_results_tib = as_tibble(fquery_results)
fquery_results_tib = fquery_results_tib %>% 
    unnest(cols = "cases", names_sep = ".")
fquery_results_tib
```
